\textbf{EECS 340: Assignment 2}

### 2020-02-03 assignment_2/article.tex
✨ Add sketch answer to Problem 2.
Co-Authored-By: bobbyCZT <zxc325@users.noreply.github.com>
✨ Add sketch justifications for answer of Problem 2.
Co-Authored-By: bobbyCZT <zxc325@users.noreply.github.com>

Since $\log (g(n_{0})) = 0$, we shall infer that $g(n_{0}) = 1$. We may arbitrarily pick some constants $c, c'}$ where:

@@

>>>>

Since $\log (g(n_{0})) = 0$, we shall infer that $g(n_{0}) = 1$. We may arbitrarily pick some constants $c, c'$ where:

@@

\paragraph{Answer}

\begin{gather}
    \frac{1}{n^a} \ll \frac{1}{n^\epsilon} \ll \log_{\frac{1}{\epsilon}}(n) \text{ \ (when $0 < \epsilon < \frac{1}{2}$)} \ll \log(n^\epsilon) \equiv \log(bn) \equiv \log(n^a) \\
    \equiv \log(n^b) \leq \log_{\frac{1}{\epsilon}}(n) \text{ \ (when $\epsilon \geq \frac{1}{2}$)} \ll (\log n)^a \ll n^{\epsilon} \\
    \ll a^{\log_a(n)} \equiv \epsilon n \equiv \frac{n}{a} \ll n^a \equiv (n+b)^a\\
    \ll (n+a)^b \ll n^{a+b} \ll \epsilon^n \ll a^{\epsilon n} \equiv a^n \ll b^n
\end{gather}

\paragraph{Justification of $\log(n^\epsilon) \equiv \log(bn) \equiv \log(n^a) \equiv \log(n^b)$\newline}

The above equations can be rewrite as:

\begin{gather}
    \log(n^\epsilon) = \epsilon \log(n) \\
    \log(n^a) = a \log(n) \\
    \log(bn) = \log(b) + \log(n) \\
    \log(n^b) = b \log(n)
\end{gather}

Where all of them can be generalized as $\Theta(\log(n))$, as it is known that $n^\epsilon \leq bn \leq n^a$ due to the decending of \textit{power(s)}.

\paragraph{Justification of $ \log_{\frac{1}{\epsilon}}(n) \text{ \ (when $0 < \epsilon < \frac{1}{2}$)} \equiv \log(n^b) \leq \log_{\frac{1}{\epsilon}}(n) \text{ \ (when $\epsilon \geq \frac{1}{2}$)}$\newline}

It is known that when $\epsilon < \frac{1}{2} \Rightarrow \frac{1}{\epsilon} \geq 2$; when $\epsilon \geq \frac{1}{2} \Rightarrow  \frac{1}{\epsilon} \leq 2$. Since it is observable that $\log_{x}(n) \gg \log_{x'}(n)$ for $x < x'$, such (in)equaility is valid.

\paragraph{Justification of $a^{\log_a(n)} \equiv \epsilon n \equiv \frac{n}{a}$\newline}

The above equations can be rewrite as:
\begin{gather}
    a^{\log_a(n)} = n^1 = \Theta(n) \\
    \epsilon n = \Theta(n) \\
    frac{n}{a} = \frac{1}{a}n =  \Theta(n)
\end{gather}

Thus, the above equality is justified.

\paragraph{Justification of $a^{\epsilon n} \equiv a^n$\newline}

We may rewrite $a^{\epsilon n}$ as the following, since there must be a $c$ for $c \in \mathbb{R^+}$ which satisfy the equality.

\begin{gather}
    a^{\epsilon} \cdot a^n = c \cdot a^n = \Theta(a^n)
\end{gather}

Since it is known that $a^n = \Theta(a^n)$, these two expressions are considered equivalent.
